\documentclass[aspectratio=169]{beamer}

\usetheme{default}
\usecolortheme{default}
\useinnertheme{rectangles}
\setbeamertemplate{navigation symbols}{}

\usepackage[T1]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{lmodern}
\usepackage{hyperref}
\usepackage[numbers]{natbib}

\definecolor{arbg}{HTML}{F6F8FB}
\definecolor{artext}{HTML}{1F2933}
\definecolor{arblue}{HTML}{204B76}
\definecolor{arteal}{HTML}{2C7A7B}
\definecolor{araccent}{HTML}{D9A441}

\setbeamercolor{background canvas}{bg=arbg}
\setbeamercolor{normal text}{fg=artext,bg=arbg}
\setbeamercolor{structure}{fg=arblue}
\setbeamercolor{frametitle}{fg=white,bg=arblue}
\setbeamercolor{title}{fg=white}
\setbeamercolor{subtitle}{fg=arbg}
\setbeamercolor{author}{fg=artext}
\setbeamercolor{date}{fg=artext}
\setbeamercolor{block title}{fg=white,bg=arteal}
\setbeamercolor{block body}{fg=artext,bg=white}
\setbeamercolor{footline}{fg=arbg,bg=arblue}
\setbeamercolor{item projected}{fg=white,bg=arteal}

\setbeamerfont{title}{series=\bfseries,size=\LARGE}
\setbeamerfont{subtitle}{size=\large}
\setbeamerfont{frametitle}{series=\bfseries,size=\large}
\setbeamerfont{block title}{series=\bfseries}

\setbeamertemplate{itemize item}{\color{arteal}\large\textbullet}
\setbeamertemplate{itemize subitem}{\color{araccent}\normalsize\textbullet}
\setbeamertemplate{blocks}[rounded][shadow=false]

\setbeamertemplate{title page}{
  \vspace*{0.08\paperheight}
  \begin{center}
  \begin{beamercolorbox}[wd=0.9\paperwidth,sep=1.2em,rounded=true,shadow=false]{frametitle}
    {\raggedright\usebeamerfont{title}\inserttitle\par}
    \vspace{0.35em}
    {\raggedright\usebeamerfont{subtitle}\insertsubtitle\par}
  \end{beamercolorbox}
  \end{center}

  \vspace{1.5em}
  {\color{araccent}\rule{0.22\paperwidth}{1.5pt}}

  \vfill

  \begin{flushleft}
    {\usebeamerfont{author}\insertauthor\par}
    \vspace{0.35em}
    {\usebeamerfont{date}\insertdate\par}
  \end{flushleft}
}

\setbeamertemplate{footline}{
  \leavevmode
  \hbox{
    \hspace*{0.02\paperwidth}
    \begin{beamercolorbox}[wd=0.96\paperwidth,ht=2.8ex,dp=1.2ex,leftskip=0.8em,rightskip=0.8em]{footline}
      \insertshorttitle\hfill\insertframenumber
    \end{beamercolorbox}
  }
}

\title{Autoresearch}
\subtitle{Autonomous Research and Software Development with LLM Agents}
\author{Ian Turner}
\date{\today}

\begin{document}

\begin{frame}
  \titlepage
\end{frame}

\begin{frame}{Why Autoresearch?}
  \begin{itemize}
    \item Large language models can already synthesize literature, write code, and iterate on plans.
    \item Agent scaffolding turns isolated model calls into longer-running workflows with memory and tools.
    \item The core question is where autonomy creates real leverage and where humans still need to stay in the loop.
  \end{itemize}
\end{frame}

\begin{frame}{Working Definition}
  \begin{block}{Autoresearch}
    The use of LLM-driven agents to perform meaningful parts of the research and engineering loop with limited direct supervision.
  \end{block}

  \vspace{0.75em}

  \begin{itemize}
    \item Gather context from papers, code, logs, and experiments.
    \item Produce artifacts such as summaries, implementations, or evaluations.
    \item Decide what to do next based on intermediate results.
  \end{itemize}
\end{frame}

\begin{frame}{Typical Loop}
  \begin{enumerate}
    \item Define an objective and success criteria.
    \item Decompose the work into research, implementation, and evaluation tasks.
    \item Use agents to collect evidence and produce candidate outputs.
    \item Review results, update the plan, and repeat.
  \end{enumerate}
\end{frame}

\begin{frame}{Concrete Example}
  \begin{itemize}
    \item Karpathy's recent \texttt{autoresearch} repository turns this loop into a concrete single-agent workflow over a small LLM training setup \citep{karpathy2026autoresearch}.
    \item The agent edits the training code, runs a bounded experiment, keeps improvements, and iterates.
    \item That makes it a useful reference point for discussing where autonomous research is already practical.
  \end{itemize}
\end{frame}

\begin{frame}{Open Questions}
  \begin{itemize}
    \item How should agents evaluate uncertainty before taking expensive actions?
    \item Which parts of software development can be reliably delegated end to end?
    \item What monitoring and control surfaces make autonomous systems auditable?
  \end{itemize}
\end{frame}

\begin{frame}{Next Steps}
  \begin{itemize}
    \item Replace example slides with project-specific claims, case studies, and results.
    \item Expand the citation set, diagrams, and benchmarks once the research narrative is settled.
    \item Extend the compile workflow further if the deck grows to include figures or custom assets.
  \end{itemize}
\end{frame}

\begin{frame}[allowframebreaks]{References}
  \footnotesize
  \bibliographystyle{plainnat}
  \bibliography{references}
\end{frame}

\end{document}
